POMDP comparisons across sigma_m, sigma_g

### 2017-12-13 appendix/appendixB.Rmd
set cores

```{r}
options(mc.cores = 4) # Reserve ~ 10 GB per core
log_dir <- "pomdp_historical"
```

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir)  %>% 
  left_join(
    select(meta, sigma_m, commonname, scenario), 
    by = c("sigma_m", "commonname")) %>% 
  arrange(scenario)
alphas <- alphas_from_log(meta, log_dir)
#models <- models_from_log(meta)
```

@@

```{r}
index <- function(x, grid) map_int(x, ~ which.min(abs(.x - grid)))
## repeats each series for each static model
ex <- examples %>%
  mutate(biomass = index(scaled_biomass, states),          
         catch = index(scaled_catch, actions))  %>% 
  left_join(policy_pars) %>% 
  ungroup() 
ex
```

```{r} 
det_f <- function(S_star, i) index(pmax(f(states,0) - S_star[[1]],0), actions)[i]
msy_f <- function(F_MSY, i) index(states * F_MSY[[1]], actions)[i]
pgy_f <- function(F_PGY, i) index(states * F_PGY[[1]], actions)[i]

@@

historical <- ex %>% 
  group_by(commonname) %>% 
  mutate(det =  det_f(S_star, biomass),
         msy =  msy_f(F_MSY, biomass),
         pgy =  pgy_f(F_PGY, biomass)) %>%
  select(year, biomass, catch, det, msy, pgy, commonname, N) %>%
  gather(model, stock, -year, -commonname, -N) %>%
  mutate(stock = states[stock] * N) %>% 
  select(-N)
```

>>>>

```{r}
options(mc.cores = parallel::detectCores()) # Reserve ~ 10 GB per core
log_dir <- "pomdp_historical"
```

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir)  %>% 
  left_join(
    ## use the estimated sigma_m, r, K pars recorded in the logged meta.csv.  Technically
    ## these should be the same as the above, but without random seed re-running the nimble
    ## code but not re-running these can create mis-matches.  
    select(meta, sigma_m, commonname, scenario),   
    by = c("sigma_m", "commonname")) %>% 
  arrange(scenario)
alphas <- alphas_from_log(meta, log_dir)
#models <- models_from_log(meta)
```

@@

```{r}
index <- function(x, grid) map_int(x, ~ which.min(abs(.x - grid)))
## repeats each series for each static model
ex <- examples %>%
  mutate(biomass = index(scaled_biomass, states),          
         catch = index(scaled_catch, actions))  %>% 
  left_join(policy_pars) %>% left_join(pars) %>%
  ungroup() 
ex
```

```{r} 
det_f <- function(S_star, r, K, i) index(pmax(gs(r[[1]],K[[1]])(states,0) - S_star[[1]],0), actions)[i]
msy_f <- function(F_MSY, i) index(states * F_MSY[[1]], actions)[i]
pgy_f <- function(F_PGY, i) index(states * F_PGY[[1]], actions)[i]

@@

historical <- ex %>% 
  group_by(commonname) %>% 
  mutate(det =  det_f(S_star, r, K, biomass),
         msy =  msy_f(F_MSY, biomass),
         pgy =  pgy_f(F_PGY, biomass)) %>%
  select(year, biomass, catch, det, msy, pgy, commonname, N) %>%
  gather(model, stock, -year, -commonname, -N) %>%
  mutate(stock = states[stock] * N) %>% 
  select(-N)
```
